\documentclass[11pt]{article}

% Use Helvetica font.
%\usepackage{helvet}

%\usepackage[T1]{fontenc}
%\usepackage[sc]{mathpazo}
\usepackage{color}
\usepackage{amsmath,amsthm,amssymb,multirow,paralist}
%\renewcommand{\familydefault}{\sfdefault}

% Use 1/2-inch margins.
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\Large \textbf{Your Project Title}

\vspace{10pt}

Project Midterm Report}

\vspace{10pt}

\textit{Team Members: xxx1, xxx2, xxx3}
\end{center}

% \linethickness{1mm}\line(1,0){498}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  Put your abstract here. It should be a brief summary of your
  task, motivation, algorithm, and results. Please keep it about
  150 words.
\end{abstract}

{\color{red} The length of your midterm report should be at least
3 pages not including references. Please replace contents with
your report contents, and then delete this paragraph.

Note that for groups with only one student, the requirement for
this midterm report length is 2 excluding references. You can
change the length of each part proportionally.}

\section{Introduction}

Use several paragraphs to introduce the background, machine
learning tasks, the dataset you use, your target machine learning
models, and your expected outcomes.

\section{Related Work}

Please briefly introduce some related works to your project. The
related work could be some papers related to your machine
learning algorithm.

Usually, this part accounts for 0.5 page. Here, you can list one
or two related works for midterm. The final version could be
finished in the final report.

\section{Your methods name}

In this section, you will introduce your machine learning
algorithms used in this part.

If you are using existing methods on a \textbf{new dataset}. You
can talk about ``dataset collection'', ``data pre-processing'',
``Feature selection'', ``Choices of hyper-parameter'',
``Evaluation metrics'', etc.

If you propose some \textbf{new methods}. You can talk about
``Drawbacks of existing methods'', ``Your proposed methods'',
``Your models based on your methods'', etc.

These are possible subsections in this part. You don't need to
include all of them. I want to see the contents that you spend
time on and have some insights.

This part is one of the most important sections. The length of this
section should be about 1.5 pages.

\section{Preliminary Results}

In this section, you will list some experimental results with
some comparisons with some baseline methods.

For example, you choose to use SVM on a new dataset. Possible
baselines would be linear perceptron and logistic regression by
using the same set of features.

In this midterm report, you can use a table to show some
preliminary results along with some discussions. This part should
be about 0.5 page.

\section{Future plan}

In this section, briefly discuss your plan based on current
achievements.

\section{References}

Please include your references here.


\end{document}
